---
title: "Probability Theory"
author: "Lucas Rousselange"
execute:
  warning: false
format:
  html:
    code-fold: true
number-sections: false
---

# Assignement 1

```{r}
P_S <- 0.3 
P_nS <- 1-P_S
P_ST <- 0.2 
P_SnT <- 1-P_ST
P_nST <- 0.6
P_nSnT <- 1-P_nST 

P_S_T <- P_S*P_ST
P_nS_T <- P_nS*P_nST
P_S_nT <- P_S*P_SnT
P_nS_nT <- P_nS*P_nSnT

```
## Given probabilities
* $P(S) = `r P_S`$
  + $P(T \mid S) = `r P_ST`$
  + $P(\overline{T} \mid S) = `r P_SnT`$
* $P(\overline{S}) = `r P_nS`$
  + $P(T \mid \overline{S}) = `r P_nST`$
  + $P(\overline{T} \mid \overline{S}) = `r P_nSnT`$

## Answer
### Probabilities
$$ 
\begin{split}
P(T \cap S) = P(S) * P(T \mid S) =`r P_S`*`r P_ST`=`r P_S_T`,\\
P(T \cap \overline{S}) = P(\overline{S}) * P(T \mid \overline{S}) =`r P_nS`*`r P_nST`=`r P_nS_T`,\\
P(\overline{T} \cap S) = P(S) * P(\overline{T} \mid S) =`r P_S`*`r P_SnT`=`r P_S_nT`,\\
P(\overline{T} \cap \overline{S}) = P(\overline{S}) * P(\overline{T} \mid \overline{S}) =`r P_nS`*`r P_nSnT`=`r P_nS_nT`. 
\end{split}
$$

### Sum of all probabilities: 
$$
P(T \cap S ) + P(T \cap \overline{S}) + P(\overline{T} \cap S) + P(\overline{T} \cap \overline{S})
= `r P_S_T+P_nS_T+P_S_nT+P_nS_nT`
$$

# Assignement 2

Q: What is the percentage of customers using all three device?  
A: $0.5 \%$


Q: What is the percentage of customers using at least two devices?  
A: $`r 7.3+3.3+8.8` \%$

Q: What is the percentage of customers using only one device?  
A: $`r 27.8+10+42.3` \%$

# Assignement 3

```{r}
P_B_A <- 0.97   #True positive rate
P_B_nA <- 0.01  #False positive rate
P_A <- 0.04     #Faulty product rate
P_nA <- 1-P_A   #Flawless product rate

P_B <- P_B_A*P_A+P_B_nA*P_nA #Total alarm trigger rate
P_A_B <- (P_B_A*P_A)/P_B #Faulty product rate when alarm triggered 
P_nA_B <- (P_B_nA*P_nA)/P_B #Flawless product rate when alarm triggered (1-P_A_B)
```

$$
\begin{split}
P(\overline{A} \mid B) = \frac{P(B \mid \overline{A})*P(\overline{A})}{P(B)}
= \frac{`r P_B_nA` * `r P_nA`}{`r P_B`} = `r round(P_nA_B, 3)`, \\
P(A \mid B) = 1 - P(\overline{A} \mid B) = 1-`r round(P_nA_B, 3)` = `r round(P_A_B, 3)`.
\end{split}
$$

*These results show that in case the alarm is triggered, there is a possibility of about **`r round(P_nA_B*100, 1)`%** that the product is **flawless** and a probability of **`r round(P_A_B*100, 1)`%** that the product is **faulty**.*
