---
title: "Causality"
author: "Lucas Rousselange"
execute:
  warning: false
format:
  html:
    code-fold: true
number-sections: false
---

# Of beauty and tomatoes 

Below you can see the correlation between the import value of tomatoes in Germany and the number of cosmetic surgeries world wide. 

## Cosmetic surgeries and tomato import value
```{r}

library(ggplot2)
library(jtools)
AB <- read.csv("../../../Causal_Data_Science_Data/AB.csv")
scale <- 0.55
y_str2 <-'Tomato import in Germany [100k€]'
y_str1 <- 'Cosmetic surgeries world wide'
p <- ggplot(AB, aes(x=Jahr, y=OP)) +
  geom_line(aes(color = y_str1)) +
  geom_line(aes(y = Wert/scale,  color = y_str2)) +
  scale_y_continuous(sec.axis = sec_axis(~.*scale, name=y_str2)) +
  labs(x = "Year", y = y_str1 )
p + theme_apa() + theme(legend.position="bottom")

```
## Correlation
```{r}
fit <- lm(AB$OP ~ AB$Wert)
fit_R2 <- cor(AB$OP, AB$Wert)
fit_R2 <- sprintf("%0.2f",fit_R2)
```
As you can imagine their is no causal link between the two. Nerveless, there is a significant correlation between both variables. The Pearson correlation coefficient is $R = `r fit_R2`$. Both samples are normaly distributed.

