---
title: "Directed Acyclic Graphs"
author: "Lucas Rousselange"
execute:
  echo: false
  warning: false
number-sections: false
---

# Task 1
The DAG for the store parking spot example only contains two nodes:

* $D$: Parking spots (Treatment variable)
* $Y$: Sales (Outcome variable)

```{r}
library(dagitty)
library(ggdag)
library(ggplot2)
dag_model <- 'dag {
D [exposure,pos="0.075,0.4"]
Y [outcome,pos="0.4,0.4"]
D -> Y
}'
# draw DAG
p <- ggdag_status(dag_model) +
  guides(fill = "none", color = "none") +  # Disable the legend
  geom_dag_edges(edge_color = "black")+
  theme_dag_blank()
p

```

# Task 2
```{r}
library(jtools)
customer_sat <- readRDS("../../../Causal_Data_Science_Data/customer_sat.rds")
lm_sat <- lm(satisfaction ~ follow_ups, data=customer_sat)
lm_sat_mod <- lm(satisfaction ~ ., data=customer_sat)
f_R <- sprintf("%0.2f",coef(lm_sat)[2])
f_R_mod <- sprintf("%0.2f",coef(lm_sat_mod)[2])
export_summs(lm_sat, lm_sat_mod)
```

# Task 3 
## Comparison
Comparing both models, we can see that our model which accounts for subscriptions has a much better accuracy than the one that does not.A coefficient reversal takes place when changing models. For our follow-up only model, the follow-up correlation coefficient is $R =`r f_R`$, while it changes to $R =`r f_R_mod`$ when subscrition model is taken into account.

### Follow-up only 
```{r}
effect_plot(lm_sat, follow_ups, interval = TRUE, plot.points = TRUE)
```

### Follow-up & Subscrition
```{r}
effect_plot(lm_sat_mod, follow_ups, interval = TRUE, plot.points = TRUE)
```
## Explanation 
A possible explanation is that the subscription is a confounding factor. Another possible explanation is that the subscription is a collision factor. The most probable explanation is that the subscription is a confounding factor, as the follow-up calls rise and the satisfaction falls with increasing subscription level. Users who use the software the most and the most features (Elite) encounter more problems and need more follow-up calls. This in turn reduces their satisfaction. 

```{r}
# Confounder
confounding <- dagify(
  X ~ Z,
  Y ~ Z,
  Y ~ X,
  coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 1, X = 0)),
  labels = list(X = "follow-ups",
                Y = "satisfaction",
                Z = "subscription")
  )

# Plot DAG
library(dagitty)
library(ggdag)
library(ggplot2)
p <- ggdag(confounding) +
  geom_dag_point(color = "#15c1d4") +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))+
  theme_dag_blank()
p
```

### Effect of subscription category on satisfaction
```{r}
effect_plot(lm_sat_mod, subscription, interval = TRUE, plot.points = TRUE , 
            jitter = 0.1)
```
### Effect of subscription category on follow-up
```{r}
lm_sub<-lm(follow_ups ~ subscription, data=customer_sat)
effect_plot(lm_sub, subscription, interval = TRUE, plot.points = TRUE , 
            jitter = 0.1)
```

# Task 4 
Here we can clearly see that the satisfaction actually increases for each group with more follow-ups.

```{r}
library(gridExtra)
# Not conditioning on education
simps_not_cond <- ggplot(customer_sat, aes(x = follow_ups, y = satisfaction)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F)+
  theme_apa()

# Conditioning on education  
simps_cond <- ggplot(customer_sat, aes(x = follow_ups, y = satisfaction, color = subscription)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  theme_apa()+
  theme(legend.position = "bottom")

# Plot both plots
#grid.arrange(simps_not_cond, simps_cond, nrow=1)
```

## Not conditioned 
```{r} 
simps_not_cond
```

## Conditioned 
```{r} 
simps_cond
```

