---
title: "Randomized Controlled Trials"
author: "Lucas Rousselange"
execute:
  warning: false
format:
  html:
    code-fold: true
number-sections: false
---

```{r}
#Load data set and libraries
library(ggplot2)
library(jtools)
library(kableExtra)
abtest_online <- readRDS("../../../Causal_Data_Science_Data/abtest_online.rds")
```


# Task 1
The covariates for which we need to check the balance are: 

* Previous site visits 
* Mobile device usage

## Previous site visits
As shown below, we can see that both groups look pretty similar, i.e. balanced with respect to previous site visits.
```{r}
compare_visits <- 
  ggplot(abtest_online, 
         aes(x = chatbot, 
             y = previous_visit, 
             color = as.factor(chatbot))) +
  geom_boxplot(width=0.3, fill="white")+
  stat_boxplot(geom = 'errorbar', width = 0.4)+
  labs(x = "Chatbot acitve", y = "Previous visits", title = 'Previous site visit balance')+
  theme_minimal()+
  theme(legend.position = "none")
compare_visits
```

## Mobile device usage
As the mobile device usage variable is a boolean, we can only compare the ratio of mobile device across both groups. Again, both groups seem balanced.
```{r}
#Calculate mobile device usage for each group
mbu_aggregate=aggregate(abtest_online$mobile_device,by=list(abtest_online$chatbot),FUN=mean)
names(mbu_aggregate)<-c('chatbot', 'mobile_device')

compare_device <- 
  ggplot(mbu_aggregate, 
         aes(x = chatbot, 
             y = mobile_device, 
             color = as.factor(chatbot))) +
  geom_boxplot(width=0.3, fill="white")+
  labs(x = "Chatbot acitve", y = "Previous visits", title = 'Mobile device usage balance')+
  ylim(0,1)+
  theme_minimal()+
  theme(legend.position = "none")
compare_device
```


# Task 2
The result of the regression is shown below:

```{r}
reg <- lm(purchase_amount ~ chatbot, abtest_online)
summ(reg)
``` 

As we can see, the chatbot has a significative negative result on the average purchase amount, albeit the fit being pretty poor.

```{r}
effect_plot(reg, chatbot)+
  labs(x = "Chatbot acitve", y = "Purchase amount", title = 'Average customer purchase amount')+
  expand_limits(y=0)
```


# Task 3 
If we account for previous visits and mobile device usage, we can see that the results of our AB test changed significantly. 
```{r}
reg_cate <- lm(purchase_amount ~ chatbot*mobile_device + chatbot*previous_visit, abtest_online)
summ(reg_cate)
``` 
# Task 4
Running a binomial regression for the effect of the chatbot on the purchase behavior of the customer, shows it has a significative negative impact on the average purchase rate.
```{r}
reg_log <- glm(purchase ~ chatbot, family=binomial(link='logit'), abtest_online)
summ(reg_log)
effect_plot(reg_log, chatbot)+
  labs(x = "Chatbot acitve", y = "Purchase rate", title = 'Average customer purchase rate')+
  ylim(0,1)
``` 
