---
title: "Matching and Subclassification"
author: "Lucas Rousselange"
execute:
  warning: false
format:
  html:
    code-fold: true
number-sections: false
---

```{r}
#Load data set and libraries
library(ggplot2)
library(tidyverse)
library(RColorBrewer)
library(dagitty)
library(ggdag)
library(jtools)
library(kableExtra)
library(MatchIt)
membership <- readRDS("../../../Causal_Data_Science_Data/membership.rds")
```

# Task 1
## Exploring the relationships

Plotting a heat map for the available factors, there seems to be a high correlation between age, average purchase and pre membership average purchase.The pre membership average purchase, age and membership card also seem correlated. The sex seems to not have a big influence on either variable.
```{r}
mem_cor <- as.data.frame(cor(membership))
mem_heat <- mem_cor %>%
  rownames_to_column() %>%
  gather(colname, value, -rowname)

ggplot(mem_heat, aes(x=colname,y=rowname, fill=value)) + 
  geom_tile(color='black')+
  scale_fill_gradient(low = "white", high = 'blue4')+
  geom_text(aes(label = round(value,2)), color = "black", size = 4) +
  labs(x='', y='', title = 'Heatmap correlation between variables')
  
```
## DAG

```{r}
# Confounder
confounding <- dagify(
  X ~ Z1,
  Y ~ Z1,
  Y ~ X,
  X ~ Z2,
  Y ~ Z2,
  Z2 ~ Z1,
  coords = list(x = c(Y = 3, Z1 = 1, X = 1, Z2=3),
                y = c(Y = 0, Z1 = 1, X = 0, Z2 =1)),
  labels = list(Z2 = "pre_avg_purch",
                Y = "avg_purch",
                Z1 = "age",
                X= 'card')
  )


p <- ggdag(confounding) +
  geom_dag_point(color = "#15c1d4") +
  geom_dag_text(color = "white") +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = label))+
  theme_dag_blank()
p

```

# Task 2
Naive model: 
```{r}
lm_naive <- lm(avg_purch ~ card, data = membership)
summ(lm_naive)
```

# Task 3
## (Coarsened) Exact Matching: 

```{r}
cem <- matchit(card ~ age + pre_avg_purch,
               data = membership, 
               method = 'cem', 
               estimand = 'ATE')
summary(cem)

df_cem <- match.data(cem)
lm_cem <- lm(avg_purch ~ card, data = df_cem, weights = weights)
summ(lm_cem)
```


## Nearest-Neighbor Matching: 
```{r}
nn <- matchit(card ~ age + pre_avg_purch,
               data = membership, 
               method = 'cem', 
               estimand = 'ATE')
summary(nn)

df_nn <- match.data(nn)
lm_nn <- lm(avg_purch ~ card, data = df_nn, weights = weights)
summ(lm_nn)
```

## Inverse Probability Weighting: 
```{r}
# (1) Propensity scores
model_prop <- glm(card ~ age + pre_avg_purch,
                  data = membership,
                  family = binomial(link = "logit"))
summary(model_prop)

# Add propensities to table
membership_aug <- membership %>% mutate(propensity = predict(model_prop, type = "response"))

# Extend data by IPW scores
membership_ipw <- membership_aug %>% mutate(
  ipw = (card/propensity) + ((1-card) / (1-propensity)))

# Run with high weights excluded
lm_ipw <- lm(avg_purch ~ card,
                data = membership_ipw %>% filter(propensity %>% between(0.15, 0.85)),
                weights = ipw)
summ(lm_ipw)
```

## Summary
```{r}
modelsummary::modelsummary(list("Naive" = lm_naive,
                                "CEM1"  = lm_cem,
                                "NN"    = lm_nn,
                                "IPW1"  = lm_ipw))
```
